%  LaTeX template for abstract submission for SAMO 2022
%
% First name and name of the speaker.
\speaker{Maximilian}{Blesch}%
%  (put no space here)
% Title of the talk, capitalized.
\title{Robust decision-making under risk and ambiguity*}

% For each author, give the first name, family name, affiliation, and email.
% Ideally, the affiliation and email should fit on a single line.
% No need to put the full snail mailing address.
%  One line per author
\author{ Maximilian }{Blesch}{Berlin School of Economics, Germany}{
maximilian.blesch@hu-berlin.de}
\author{Philipp}{Eisenhauer}{University of Bonn, Germany}{peisenha@uni-bonn.de}


% Type your abstract here.
\abstract{%Include your abstract here. You can give references  like here \cite{ref1} or \cite{ref2}.
%Recall that if you need to define your own macros, it is required to include your name in their definitions. \textbf{(1,000 words and 2 pages maximum)}
Decision-makers often confront uncertainties when determining their course of action. For example, individuals save to cover uncertain medical expenses in old age \cite{French.2014}. Firms set prices facing uncertainty about their competitive environment \cite{Ilut.2020}, and policy-makers vote for climate change mitigation efforts facing uncertainty about future costs and benefits \cite{Barnett.2020}. We consider the situation where a decision-maker posits a collection of economic models to inform his decision-making process. Each model formalizes the objectives and trade-offs involved. Within a given model, uncertainty is limited to risk as a model induces a unique probability distribution over possible futures. In addition, however, there is also ambiguity about the true model \cite{Arrow.1951,Knight.1921}.\\

In this context, we focus on the common practice in economics to estimate a subset of the model parameters outside the model and let the decision-makers inside the model treat these point estimates as-if they correspond to the true parameters.
% \footnote{See for example \cite{Berger.2015}, \cite{Blundell.2016}, \cite{Cagetti.2006}, \cite{Chiappori.2018}, \cite{DeNardi.2010}, \cite{Ejrnaes.2020},  \cite{Fernandez.2014}, \cite{French.2011}, \cite{Gourinchas.2002}, \cite{Huo.2020}, \cite{Scholz.2006}, \cite{Sommer.2016}, and  \cite{Voena.2015}.}
This approach ignores ambiguity about the true model, resulting from the parametric uncertainty of the first-step estimation, and opens the door for the misspecification of the decision problem. As-if decision-makers, decision-makers who use the point estimates to inform decisions that would be optimal if the estimates were correct \cite{Manski.2021}, face the risk of serious disappointment about their decisions. The performance of as-if decisions often turns out to be very sensitive to misspecification \cite{Smith.2006}, which is particularly consequential in dynamic models where the impact of erroneous decisions accumulates over time \cite{Mannor.2007}. This danger creates the need for robust decision rules that perform well over a whole range of different models instead of an as-if decision rule that performs best for one particular model. However, increasing robustness, often measured by a performance guarantee under a worst-case scenario, decreases performance in all other scenarios. Striking a balance between the two objectives is challenging.\\

We develop a framework to evaluate as-if and robust decision rules in a decision-theoretic setting by merging insights from the literature on data-driven robust optimization \cite{Bertsimas.2018} and robust Markov decision processes \cite{Ben-Tal.2009} with statistical decision theory \cite{Berger.2010}. We set up a stochastic dynamic investment model where the decision-maker takes ambiguity about the model's transition dynamics directly into account. We construct ambiguity sets for the transitions that are anchored in empirical estimates, statistically meaningful, and computationally tractable \cite{Ben-Tal.2013} using the Kullback-Leibler divergence \cite{Kullback.1951}. Our work brings together and extends research in economics and operations research to make econometrics useful for decision-making with models \cite{Manski.2021,Bertsimas.2006}.\\

As an application, we revisit \cite{Rust.1987}'s seminal bus replacement problem which serves as a computational illustration in a variety of settings.\footnote{See for example \cite{Christensen.2019}, \cite{Iskhakov.2016}, \cite{Reich.2018}, and \cite{Su.2012a}.}  In the model, the manager Harold Zurcher implements a maintenance plan for a fleet of buses. He faces uncertainty about the future mileage utilization of the buses. To make his plan, he assumes that the mileage utilization follows an exogenous distribution and uses data on past utilization for its estimation. In the standard as-if analysis, the distribution is estimated in a first step and serves as a plug-in for the true unknown distribution. Harold Zurcher makes decisions as-if the estimate is correct and ignores any remaining ambiguity about future mileage utilization. We set up a robust version of the bus replacement problem to directly account for the estimation uncertainty and explore alternative decision rules' properties and relative performance.\\

In econometrics, there is burgeoning interest in assessing the sensitivity of findings to model or moment misspecification.\footnote{See for example \cite{Andrews.2020}, \cite{Andrews.2017}, \cite{Armstrong.2021}, \cite{Bonhomme.2020}, \cite{Chernozhukov.2020},  \cite{Christensen.2019}, and \cite{Honore.2020}.} Our work is most closely related to \cite{Jorgensen.2021}, who develops a measure to assess the sensitivity of results to fixing a subset of parameters of a model prior to the estimation of the remaining parameters. Our approach differs as we directly incorporate model ambiguity in the design of the decision-making process inside the model and assess the performance of a decision rule under misspecification of the decision environment. As such, our focus on ambiguity faced by decision-makers inside economic models draws inspiration from the research program summarized in \cite{Hansen.2016} that tackles similar concerns with a theoretical focus. We complement recent work by \cite{Saghafian.2018}, who works in a setting very similar to ours but does not use statistical decision theory to determine the optimal robust decision rule. In ongoing work, \cite{Eisenhauer.2021} use statistical decision theory to structure policy decisions in light of uncertainty about counterfactual policy predictions due to the remaining parametric uncertainty after the estimation of a model. They conduct an ex-post evaluation of alternative policy proposals using decision-theoretic criteria. We, on the other hand, perform a proper ex-ante analysis of competing decision rules. We evaluate each rule's performance under all possible parameterizations of the model and directly account for parametric uncertainty in their construction. In operations research, there exists a small number of applications of data-driven robust decision-making in a dynamic setting, which include portfolio allocation \cite{Zymler.2013}, elective admission to hospitals \cite{Meng.2015}, scheduling of liver transplantation \cite{Kaufman.2017}, and the cost-effectiveness of colorectal cancer screening policies \cite{Goh.2018}. To the best of our knowledge, none evaluates the performance of robust decisions against the as-if alternative in a decision-theoretic framework.\


%  If you have references, put them here in a format like below.
%  This can be obtained using BiBTeX with the bib style plain.bst, uncommenting first the two next lines and replacing them by the generated .bbl file
\newpage
\bibliographystyle{plain}
\bibliography{literature.bib}
%
%  Note that this bibliography must be placed inside the abstract.
%\begin{thebibliography}{1}


%\bibliography{literature.bib}
%\bibitem{ref1}
%P. Name.
%\newblock Paper {T}itle.
%\newblock {\em Journal Title},  X (x): 1--12, Year.

%\bibitem{ref2}
%D.~Name2.
%\newblock {\em Book Title}.
%\newblock Publisher, Year.

%\end{thebibliography}
}  % End of abstract.
